 \section*{Discussion}

\plr{
    JRI: Somewhere, put discussion of future work with crosses
    for figuring out what's going on in selection on standing variation
    (what are questions? (pleiotropy?) methods?)
    framed in part like "what should everyone else do".
}

Our analysis of diversity and population structure in maize landraces from Mesoamerica and S. America points to an independent origin of S. American highland maize, in line with earlier archaeological \cite[]{Piperno_2006_69,Perry_2006_16511492,Grobman_2012_22307642} and genetic \citep{vanHeerwaarden_2011_21189301} work. 
We use our genetic data to fit a model of historical population size change, and find 
%no evidence of a bottleneck in Mesoamerica but 
evidence of a strong bottleneck followed by expansion in the highlands of S. America. 
\st{In our model, the domestication bottleneck was also incorporated, following \cite{Wright_2005_15919994}.
Note that we relied on the previous estimation of the strength of the domestication bottleneck, but
we also confirmed that the change of the strength of the bottleneck had almost no influence on the null distributions of $F_{ST}$ values (not shown).  In other words, our conclusion of rare convergent adaptation at the molecular levels is robust against the strength of the domestication bottleneck.}


\st{ {\bf Delete this para later} Surprisingly, our models showed no support for a maize domestication bottleneck, apparently contradicting earlier work \cite[]{Eyre-Walker_1998_9539756,Tenaillon_2004_15014173,Wright_2005_15919994}. 
One factor contributing to these differences is the set of loci sampled. 
Previous efforts focused on data exclusively from protein-coding regions, while our data set includes a large number of noncoding variants.
Diversity differences between maize and teosinte are greatest in protein-coding regions \citep{Hufford_2012_22660546}, presumably due to the effects of background selection \citep{Charlesworth_1993_8375663}, and demographic estimates using only protein-coding loci should thus overestimate the strength of a domestication bottleneck.
While a more detailed comparison with data from teosinte will be required to validate these results, they nonetheless suggest the value of a reassessment of the combined impacts of demography and selection on genome-wide patterns of diversity during maize domestication.}

We identified SNPs deviating from patterns of allele frequencies determined by our demographic model as loci putatively under selection for highland adaptation.
These conclusions are supported by evidence of haplotype differentiation (Table~\ref{supp:phs}) and the directionality of allele frequency change (Supporting Information, File S1).
Consistent with results from both GWAS \citep{Wallace_2014_25474422} and local adaptation in teosinte \citep{Pyhajarvi2013}, we find that putatively adaptive SNPs are enriched in intergenic regions of the genome, further suggesting an important role for regulatory variation in maize evolution. 

Although our data identify hundreds of loci that may have been targeted by natural selection in Mesoamerica and S. America, 
fewer than 1.8\% of SNPs and 2.1\% of genes show evidence for convergent evolution between the two highland populations.
This relative lack of convergent evolution is concordant with recently developed theory \citep{ralph2014convergent},
which applied to this system suggests that convergent evolution involving identical nucleotide changes 
is unlikely to have occurred in the time since domestication through either recurrent mutation or migration across Central America via seed sharing.   
These results are generally robust to variation in most of the parameters, but are sensitive to gross misestimation of some of the parameters -- for example if seed sharing was common over distances of hundreds of kilometers.  
The modeling highlights that our outlier approach may not detect traits undergoing convergent evolution 
if the genetic architecture of the trait is such that mutation at a large number of nucleotides would have equivalent effects on fitness 
(i.e. adaptive traits have a large mutational target). 
While QTL analysis suggests that some of the traits suggested to be adaptive in highland conditions may be determined by only a few loci \citep{Lauter_2004_15342532}, 
others such as flowering time \citep{buckler2009genetic} are likely to be the result of a large number of loci, each with small and perhaps similar effects on phenotype.  
Future quantitative genetic analysis of highland traits using genome-wide association methods may prove useful in searching for the signal of selection on such highly quantitative traits. 

Our observation of little convergent evolution is also consistent with the possibility that much of the adaptation to highland environments made use of standing genetic variation in lowland populations. 
Indeed, we find that as much as 90\% of the putatively adaptive variants in Mesoamerica and S. America are segregating in lowland populations, 
and the vast majority are also segregating in teosinte.  
Selection from standing variation should be common when the scaled mutation rate $\Theta$ 
(product of the effective population size, mutation rate and target size) is greater than 1,
as long as the scaled selection coefficient $Ns$ 
(product of the effective population size and selection coefficient) is reasonably large \cite[]{Hermisson_2005_15716498}.
Estimates of $\theta$ from synonymous nucleotide diversity in maize are around 0.014, \citep{Tenaillon_2004_15014173,Wright_2005_15919994,Ross-Ibarra_2009_19153259}, 
suggesting that adaptation from standing genetic variation may be likely for target sizes larger than a few hundred nucleotides.
In maize, such a scenario has been recently shown for the locus \emph{grassy tillers1} \cite[]{Wills_2013_23825971}, at which adaptive variants in both an upstream control region and the 3' UTR are segregating in teosinte but show evidence of recent selection in maize, presumably due to the effects of this locus on branching and ear number.

\plr{something about: 
    Much of the variation present in the founding pops of the two highlands was likely shared,
    but we still reasonably might not expect to see shared $F_{ST}$ signals,
    because (a) for quantitative traits don't expect to see much anyhow;
    and (b) which alleles are $F_{ST}$ outliers is very dependent on initial allele frequencies,
    and hence fairly random.
    Also, as Nick says: ``It seems more plausible that adaptation is from standing variation, but picks up different allelic combinations in different high-altitude populations.  That is not at all unlikely, either by chance or because of epistasis which allows the same phenotype to come from different (and incompatible) gene combinations.  Actually, crossing experiments between high-altitude populations would be most informative here.''
}

Finally, although we evaluated a genome-wide sample of more than 90,000 SNPs, this sampling is likely insufficient to capture all of the signals of selection across the genome.  
Linkage disequilibrium in maize decays rapidly \citep{Chia_2012_22660545}, reaching a plateau in only a few hundred bp (Figure~\ref{supp:LD}) and a much greater density of SNPs would be needed to effectively identify the majority of selective sweeps in the history of these populations \cite[]{tiffin2014advances}.
SNP density alone does not explain the lack of convergent evolution seen at SNPs showing evidence of selection, however.  
Our genomic sampling may have thus identified only a subset of all loci targeted by natural selection, but there is no reason to believe that the percentage of selected loci showing convergent selection should change with higher genotyping density. 

%\label{other taxa}
%The rarity of convergent evolution in maize contrasts with data from humans \citep{Tennessen_2011_21698142} showing selection on the same genes in multiple pairs of tropical and temperate populations.  
%However, in both maize and humans the majority of adaptive variants appear to have been derived from standing variation \cite[]{Tennessen_2011_21698142}.
%One difference between these two species is effective population size: the effective population size of maize ($\sim10^5$) is an order of magnitude larger than that in humans \cite[]{Takahata_1997_9114074}.
%Humans would therefore have less standing variation as a source of adaptation, perhaps resulting in the same variants being selected in multiple subpopulations (as long as $s$ is sufficiently large and initial frequency is, for example, $>0.1$).
%In contrast, maize could maintain a larger number of adaptive variants in the ancestral lowland population.
%In this case, if genetic variants produce similar phenotypic effects, they may be selected to high frequency in independent highland regions at random.
%Or if Mexican and S. American highlands have slightly different climates, it is feasible that different variants are selected.






%Recent empirical examples of adaptation from standing variation \cite[Reviewed in ][]{Barrett_2008_18006185,Messer_2013_24075201} and detection of soft selective sweeps in Drosophila \cite[]{Garud_2013_ArXiv} and humans \cite[]{Turchin_2012_22902787,Peter_2012_23071458} suggest this may be a common form of adaptation.




